---
title: "Report on the first name LOUIS"
author: "Your name"
date: "10-02-2023"
format: html
editor: source
theme: "cosmo"
---

### 1. Setup

The packages needed in a qmd must *always* be loaded in a code chunk at the beginning of the file.

```{r, message = F, warning = F}
library(dplyr)
library(tidyverse)
library(ggplot2)
library(here)
```

However, the command `install.packages()` must **not** be written in a Quarto document.\
It should be run only once in the console.

### 2) Data cleaning

```{r}
names <- read.csv(
  here("data", "fichier_prenoms.csv"),
  sep = ";",
  encoding = "UTF-8"
)

names <- names %>% 
  mutate(Gender = ifelse(sexe == 1, "Male", "Female")) %>% 
  filter(annais != "XXXX") %>% 
  mutate(Year = as.numeric(annais)) 
```

### 3) Evolution of the first name LOUIS over time

```{r, echo = F, message = F, fig.height = 3, fig.width = 8}
names %>% filter(preusuel == "LOUIS") %>%
  group_by(Year, Gender) %>%
  summarise(Total = sum(nombre)) %>% ungroup() %>%
  ggplot(aes(x = Year, y = Total, color = Gender)) + geom_line()
```

```{r, echo = F}
n_louis <- names %>% filter(Year == 2021 & preusuel == "LOUIS") %>% summarise(n = sum(nombre))
```

`r n_louis$n` children were born under the name LOUIS in 2021. This statistic is written in\
inline code such that it updates automatically.

## Part 2 - Latex

$Y_i = \alpha + \beta X_i + \varepsilon_i$

$\hat{Y_i}$ denote the fitted values of the model.